\documentclass[a4,11pt]{article}
\usepackage{tikz} %to draw models
\usetikzlibrary{tikzmark}
\usepackage{multicol} %for multi columns
\usepackage{xcolor} %for color
\usepackage[utf8]{inputenc}
\usepackage{gb4e}
\usepackage{enumitem}
\usepackage{amsmath} %for fractions
\usepackage{fullpage}
\usepackage{graphicx}
\graphicspath{ { } }


\setlength{\parindent}{0in}

\definecolor{Pink}{RGB}{240,0,120}
\newcommand{\jt}[1]{\textbf{\textcolor{Pink}{#1}}}


\title{Week 5: Quiz questions and model answers}
\author{Judith Tonhauser and Elena Vaik\v snorait\.{e} }
\date{\today}

\begin{document}

\maketitle

{\bf Introductory message:} This quiz covers the material in CC section 2.4. This section discusses licensing environments for negative polarity items (NPIs). This quiz test your knowledge of set theory (based on the previous chapter) and identifying whether an expression is downward entailing.

% An expression licenses NPIs wherever it licenses downward entailments (p.62)

% negative polarity items: defined as a word that is acceptable in a sentence with sentential negation but unacceptable in the positive variant
% distribution of NPIs: need to be able to talk about environments where NPIs are acceptable, e.g.,:
%	- argument of preposition
%	- clause-mate to adverb, 
%	- complement clause, 
%	- restriction of quantifier, scope of quantifier

% upward entailment, downward entailment
% semantic value of the NP musician is the set of musicians
% semantic value of the NP cellist ist the set of cellists
% subset relation, downward entailment

\begin{enumerate}[leftmargin = 12pt]

\item {\bf Eulid diagram} A  the set of dogs. B is the set of all entities that like Whiskas. Which sentence does the Eulid diagram capture?

\begin{tikzpicture}[fill=gray]
% left hand
\scope
\clip (-2,-2) rectangle (2,2)
      (1,0) circle (1);
\fill (0,0) circle (1);
\endscope
% right hand
\scope
\clip (-2,-2) rectangle (2,2)
      (0,0) circle (1);
\fill (1,0) circle (1);
\endscope
% outline
\draw (0,0) circle (1) (0,1)  node [text=black,above] {$A$}
      (1,0) circle (1) (1,1)  node [text=black,above] {$B$}
     (-2,-2) rectangle (3,2) node [text=black,above] {};
\end{tikzpicture}

      \begin{enumerate}[noitemsep]
        \item \textit{Some dogs likes Whiskas.} (1pt checked / -1pt unchecked)
	\item \textit{No dog likes Whiskas.} (-1pt checked / 1pt unchecked)
        \item \textit{Every dog likes Whiskas.} (-1pt checked / 1pt unchecked)
	\end{enumerate}	

{\bf Model answer:}  The correct answer is \textit{Some dogs likes Whiskas}, since the intersection between the set of dogs and the set of entities that like Whiskas is not empty.


\item {\bf Sets 1} A  the set of dogs. B is the set of all entities that like Whiskas. Which formula captures the meaning of the sentence \textit{No dog likes Whiskas.}

      \begin{enumerate}[noitemsep]
        \item A $\cap$ B = $\emptyset$ (1pt checked / -1pt unchecked)
	\item A $\cup$ B = $\emptyset$  (-1pt checked / 1pt unchecked)
        \item A $\subset$ B (-1pt checked / 1pt unchecked)
	\end{enumerate}	
	
{\bf Model answer:}  The correct answer is  A $\cap$ B = $\emptyset$, since the intersection of dogs and likers of Whiskas is empty. 


\item {\bf Sets 2} A  the set of parrots. B is the set of all entities that like to sing. Which formula captures the meaning of the sentence \textit{Every parrots likes singing.}

        \begin{enumerate}[noitemsep]
        \item A $\cap$ B = $\emptyset$ (1pt checked / -1pt unchecked)
	\item A $\cup$ B = $\emptyset$  (-1pt checked / 1pt unchecked)
        \item A $\subset$ B (-1pt checked / 1pt unchecked)
	\end{enumerate}	

{\bf Model answer:}  The correct answer is  A $\subset$ B. Since every member of the set of parrots is a member of the set of entities who like singing.

\item {\bf Monotonicity: Every} The quantifier \textit{every} is left downward monotone. Given sentence \textit{Every human uses Twitter}, come up with a version of the sentence that shows that  \textit{every} is left downward monotone
	
{\bf Model answer:} To show that an expression is left downward monotone, one needs to come up with a version of a sentence where human is substituted with a different expression that refers to subset of the set human, e.g. politician, woman, astronaut etc. If the entailment holds between two sentences, then  \textit{every} is left downward monotone.


\item {\bf Monotonicity: No} The quantifier \textit{no} right downward monotone because the sentence \textit{No dog likes to sleep} entails:

      \begin{enumerate}[noitemsep]
        \item \textit{No dog likes to sleep on the ground} (1pt checked / -1pt unchecked)
	\item \textit{No poodle likes to sleep} (-1pt checked / 1pt unchecked)
        \item \textit{Noone likes to sleep} (-1pt checked / 1pt unchecked)
	\end{enumerate}	

{\bf Model answer:}  The correct answer is \textit{No dog likes to sleep on the ground}. A right downward monotone determiner is a determiner such that in a sentence of the form D X Y it entails D X Y', where Y' is a subset of Y. \textit{Sleep on the ground} is a subset of \textit{sleep}. The sentence \textit{No poodle likes to sleep} shows that \textit{no} is also left downward monotone, because a poodle is a subset of dogs.

\item {\bf Monotonicity: Few} Based on the sentences below, determine whether \textit{few} is downward monotone. Select all that apply. 

\begin{itemize}[noitemsep]
\item Few athletes play piano.
\item Few footballers play piano.
\item Few athletes play piano well.
\end{itemize}

      \begin{enumerate}[noitemsep]
        \item Left downward monotone (1pt checked / -1pt unchecked)
        \item Right downward monotone (1pt checked / -1pt unchecked)
        \item Not downward monotone (-1pt checked / 1pt unchecked)
	\end{enumerate}	

{\bf Model answer:} The correct answers are left and right downward monotone. If \textit{Few athletes play piano} is true, then it means that \textit{few footballers play piano.} is also true. Since footballers is a subset of athletes, few is left downward monotone. If \textit{Few athletes play piano} is true, then it is also true that \textit{few athletes play piano well}, since the set containing all entities that play piano well is a subset of  the set that contains all entities that play piano.


\item {\bf Monotonicity: All} Based on the sentences below, determine whether \textit{all} is downward monotone. Select all that apply. 
\begin{itemize}[noitemsep]
\item All dogs love walks.
\item All chihuahuas love walks.
\item All dogs love walks in a park.
\end{itemize}


      \begin{enumerate}[noitemsep]
        \item Left downward monotone (1pt checked / -1pt unchecked)
        \item Right downward monotone (-1pt checked / 1pt unchecked)
        \item Not downward monotone (-1pt checked / 1pt unchecked)
	\end{enumerate}	
	

{\bf Model answer:} The correct answer is left downward monotone. If \textit{All dogs love walks} is true, then it means that \textit{all chihuahuas love walks} is also true. Since chihuahuas is a subset of dogs, \textit{all} is left downward monotone. If \textit{All dogs love walks} is true, it does not entail that \textit{all dogs love walks in a park} is true. Some dogs might prefer walks in a city center. Therefore, \textit{all} is not right downward monotone.

\item {\bf Sets: 3}  A is a set of dogs. B is a set of all entities that like Whiskas. C is a set of snorers. The following sentences are true. 

\begin{itemize}[noitemsep]
\item No dog like Whiskas.
\item Some dogs are snorers.
\item Everyone who likes Whiskas is a snorer.
\end{itemize}

Select all true statements in set-theoretic notation. (Grading: multiple choice; 1pt if correct, -1pt if incorrect)

\begin{enumerate}
\item A $\cap$ B $\neq$ $\emptyset$
\item A $\cap$ B = $\emptyset$
\item A $\cap$ C $\neq$ $\emptyset$
\item A $\cap$ C = $\emptyset$
\item A $\subseteq$ C 
\item B $\subseteq$ C 
\item C $\subseteq$ B
\end{enumerate}

{\bf Model answer:} The correct answers are (b), (c), (f). (b) captures the sentence \textit{No dog like Whiskas}, i.e. the intersection of dogs and entities that like Whiskas is empty. (c) captures the sentence \textit{some dogs are snorers}, i.e. the intersection of dogs and is not empty. (f) captures the sentence \textit{Everyone who likes Whiskas is a snorer}.

(a) is false, it would be true if some dogs liked Whiskas. (d) is false, it would be true if no dog snored. (e) is false, it would be true if all dogs were snorers. (g) is false, it would be true, if all snorers would be Whiskas-lovers.

\end{enumerate}
\end{document}
