\documentclass[11pt,fleqn,a4paper/thesis]{article}
\usepackage[margin=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{tikz}
\usepackage{mathtools}
\usepackage{longtable}
\usepackage{enumitem}
\usepackage{hyperref}
%\usepackage[dvips]{graphics}
%\usepackage[table]{xcolor}
%\usepackage{amssymb}
\usepackage{float}
%\usepackage{subfig}
\usepackage{booktabs}
\usepackage{subcaption}

\usepackage[normalem]{ulem}

\expandafter\def\expandafter\UrlBreaks\expandafter{\UrlBreaks%  save the current one
  \do\a\do\b\do\c\do\d\do\e\do\f\do\g\do\h\do\i\do\j%
  \do\k\do\l\do\m\do\n\do\o\do\p\do\q\do\r\do\s\do\t%
  \do\u\do\v\do\w\do\x\do\y\do\z\do\A\do\B\do\C\do\D%
  \do\E\do\F\do\G\do\H\do\I\do\J\do\K\do\L\do\M\do\N%
  \do\O\do\P\do\Q\do\R\do\S\do\T\do\U\do\V\do\W\do\X%
  \do\Y\do\Z}

\usepackage{multicol}
\usepackage{txfonts}
\usepackage{amsfonts}
\usepackage{natbib}
\usepackage{gb4e}
\usepackage[all]{xy}
\usepackage{rotating}
\usepackage{tipa}
\usepackage{multirow}
\usepackage{authblk}
\usepackage{url}
\usepackage{pdflscape}
\usepackage{rotating}
\usepackage{adjustbox}
\usepackage{array}

\def\bad{{\leavevmode\llap{*}}}
\def\marginal{{\leavevmode\llap{?}}}
\def\verymarginal{{\leavevmode\llap{??}}}
\def\swmarginal{{\leavevmode\llap{4}}}
\def\infelic{{\leavevmode\llap{\#}}}

\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
%\definecolor{gray}{rgb}{0.36, 0.54, 0.66}

\newcommand{\dashrule}[1][black]{%
  \color{#1}\rule[\dimexpr.5ex-.2pt]{4pt}{.4pt}\xleaders\hbox{\rule{4pt}{0pt}\rule[\dimexpr.5ex-.2pt]{4pt}{.4pt}}\hfill\kern0pt%
}

\setlength{\parindent}{0in}
\setlength{\parskip}{1ex}

\newcommand{\yi}{\'{\symbol{16}}}
\newcommand{\nasi}{\~{\symbol{16}}}
\newcommand{\hina}{h\nasi na}
\newcommand{\ina}{\nasi na}

\newcommand{\foc}{$_{\mbox{\small F}}$}

\hyphenation{par-ti-ci-pa-tion}

\setlength{\bibhang}{0.5in}
\setlength{\bibsep}{0mm}
\bibpunct[:]{(}{)}{,}{a}{}{,}

\newcommand{\6}{\mbox{$[\hspace*{-.6mm}[$}} 
\newcommand{\9}{\mbox{$]\hspace*{-.6mm}]$}}
\newcommand{\sem}[2]{\6#1\9$^{#2}$}
\renewcommand{\ni}{\~{\i}}

\newcommand{\citepos}[1]{\citeauthor{#1}'s \citeyear{#1}}
\newcommand{\citeposs}[1]{\citeauthor{#1}'s}
\newcommand{\citetpos}[1]{\citeauthor{#1}'s (\citeyear{#1})}

\newcolumntype{R}[2]{%
    >{\adjustbox{angle=#1,lap=\width-(#2)}\bgroup}%
    l%
    <{\egroup}%
}
\newcommand*\rot{\multicolumn{1}{R{90}{0em}}}% no optional argument here, please!


\title{Guidelines for term papers and theses}

\author{Judith Tonhauser}
\affil{University of Stuttgart}

\renewcommand\Authands{ and }

\newcommand{\jt}[1]{\textbf{\color{blue}JT: #1}}

\begin{document}

\maketitle

\section{Introduction}

This document provides detailed information on the content and organization of papers and theses in linguistics, as well as on the styles and conventions (``mechanics'') for such works. It thereby also provides information on how such works will be assessed. 

The current document expands on the following document, referred to below as the ``IfLA document'', which also provides information on papers and theses in linguistics: 

\url{https://www.ling.uni-stuttgart.de/institut/ifla/PDF_Upload/Allgemeine-Info/FormblattHaus-Abschlussarbeiten_IfLA_2019_neu.pdf}

Please take particular note of the extensive guidelines in the IfLA document on the style of referencing in linguistics (sections 3 and 4)!

Your term paper/thesis will be graded on the following scale: 

\setlength{\tabcolsep}{20pt}
\begin{tabular}{rrrr}
100-95,5 points: 1,0 & 87-83,5 points: 2,0 & 75-71,5 points: 3,0 & 63-60 points: 4,0  \\ 
95-91,5 points: 1,3 & 83-79,5 points: 2,3  & 71-67,5 points: 3,3 & 59-0 points: 5,0 \\
91-87,5 points: 1,7 & 79-75,5 points: 2,7 & 67-63,5 points: 3,7 & \\
\end{tabular}

Of the 100 possible points, 70 are allotted to content, 20 to organization and 10 to mechanics.

\section{Content (70 points)}

To receive full credit:

\begin{itemize}[itemsep=-1pt,leftmargin=2.5ex,topsep=-2pt]

\item All of the sentences can be interpreted and the content of each sentence pertains to the topic of the paper/thesis.

\item The paper/thesis is appropriate to read for somebody who has taken an introduction to linguistics, but is not familiar with the topic to which your research question pertains. In particular, the paper/thesis is not written for your instructor/advisor, who is very familiar with the topic.

\item Background on the topic is properly introduced, the empirical phenomenon is introduced and illustrated with examples, and terminology is defined and exemplified on its first use. 

\item The paper/thesis has an informative title, pertaining to the research question (not, e.g., {\em Research paper for Advanced Semantics} or {\em My thesis}).

\item The paper/thesis is written in a scientific manner: claims are supported by empirical evidence and/or references, and hypotheses are identified as such. Personal opinions are not included. The paper/thesis does not include flowery language (e.g., {\em These data are very interesting}), inessential information (e.g., {\em Language is a tool for human communication}), information about the process of developing the paper (e.g., {\em I started to wonder about X, and then I decided to work on it.}), or information about how the author feels about the research (e.g., {\em This research was difficult to conduct}) or personally relates to the research (e.g., {\em I'm interested in this work because my brother used to say...}).

\item The works cited are peer-reviewed books, journal articles or conference papers; wikipedia, newspaper articles and the like are not peer-reviewed and therefore typically not appropriate. (You can identify suitable peer-reviewed works by searching key words pertaining to your research topic in the {\em Modern Language Association} (MLA) database, to which the University of Stuttgart provides you access: go to the UB webpage, then to the `Katalog  der UB', search for ``MLA International Bibliography'', e.g., in Titelwort, and you will find the link to the MLA database.)

\item Using ChatGPT, or other such tools, to write your papers/thesis is not allowed: If text produced by ChatGPT is included in your paper/thesis and is not attributed to ChatGPT,  then this constitutes plagiarism because the text is not your own words or ideas. Attributing parts of your paper/thesis to ChatGPT is not allowed because the content produced by ChatGPT is not peer-reviewed (see previous bullet).

\item All examples, figures and tables are discussed in the main body of the text; the paper/thesis does not expect the reader to figure out by themselves what they show. Examples, figures and tables occur in the main body of the text (not, for instance, at the end), at the place when they are most useful to the reader.

\item The language used in the paper/thesis is inclusive (\url{https://www.linguisticsociety.org/resource/guidelines-inclusive-language}). For instance, speakers and listeners are not exclusively male, and examples do not only have male subjects acting on female objects.

\item Each chapter, section, subsection, etc.\ contains the content that the reader expects for that chapter, section, subsection, etc. Which chapters and sections your work includes depends on the type of work.  There are two types of works: i) a state-of-the-art paper/thesis, and ii) a research paper/thesis. Be sure to follow the guidelines for whichever type of paper/thesis you are writing:

\begin{enumerate}

\item {\bf State-of-the-art paper/thesis}

The paper/thesis presents the state-of-the-art on a research question. As such, it first states and motivates the research question (`introduction', section 1), it then summarizes prior research on the research question (`prior research', section 2), it then synthesizes and critiques that prior research with respect to the research question (`Critical discussion', section 3), and then it concludes with a summary of the paper (`conclusions', section 4).

\begin{itemize}[leftmargin=2.5ex,topsep=-2pt]

\item Introduction: What is the research question? How is the research question motivated?

The research question is not necessarily presented in the first sentence of the paper/thesis. In fact, in most cases, it is first necessary to gently introduce the reader to the phenomenon discussed in the paper and the topic of the paper, by using examples, clarifying terminology, and introducing relevant background, before the research question can be stated. The introduction also provides a brief overview of the sections of the paper/thesis.

\item Prior research: How have prior works addressed the research question? 

This section presents relevant prior literature in sufficient detail to allow the reader to understand the research question, methodology, and results of that work, and how it is relevant to the research question addressed in the paper/thesis. Only those aspects of the prior work should be presented that are relevant to the research question or to the reader's understanding of the work. Terminology used in prior literature is defined and illustrated, or (when appropriate) replaced by terminology used in your paper/thesis. Works are summarized and critiqued (e.g., {\em Tonhauser 2018 claimed that...}), not the researchers (e.g., {\em Tonhauser claimed that...}). 

\item Critical discussion: What are the results emerging from this literature with respect to the research question? What are the implications of these results?

This section critically discusses and synthesizes the research presented in the previous section. You may critique literature presented in the previous section, in ways that are relevant to the research question. What the section should definitely do is offer the reader higher-level evaluations of the literature presented in the previous section, with respect to the research question, addressing questions such as: How does the literature differ (or not) in framing the research question/From which perspective does the literature engage with the research question? Which terminology is used in the prior literature, and how does it relate? How do the results obtained in the prior literature with respect to the research question compare? (Give the reader an overview.) Are the differences in terminology, methodology, results, etc. superficial or do they relate to substantial differences in perspective on the research question, or reveal fundamental disagreements in the literature? Which results does the literature agree or disagree on? How do the methods used in the prior literature relate? What are advantages/disadvantages of the various methods? Which questions are left open, and how might they be addressed next? Make sure that the discussion is sufficiently contextualized, and that you guide the reader through the individual parts of the discussion (possibly with the help of sections/subsections, and appropriate signposting).

\item Conclusions: Which research question was investigated, what are the main results, and which next questions arose?

The concluding section/chapter minimally states the research question and briefly summarizes the results and the implications. It can also mention future research directions. 

\end{itemize}

\item {\bf Research paper/thesis}

The paper/thesis presents an investigation of a research question. As such, it first states and motivates the research question (`introduction', section 1), it then contextualizes the research question (`prior research', section 2), it then presents your empirical investigation of the research question, including the results of that investigation (`empirical investigation', section 3), it then discusses implications of the results (`discussion', section 4), and it then concludes with a summary of the research conducted on the research question (`conclusions', section 5).

\begin{itemize}[leftmargin=2.5ex,topsep=-2pt]

\item Introduction: What is the research question? How is the research question motivated?

The research question is not necessarily presented in the first sentence of the paper/thesis. In fact, in most cases, it is first necessary to gently introduce the reader to the phenomenon discussed in the paper and the topic of the paper, by using examples, clarifying terminology, and introducing relevant background, before the research question can be stated. The introduction also tells the reader (briefly) about the result of the investigation, and provides a brief overview of the sections of the paper/thesis. (You are not writing a crime novel, so it is not necessary to create suspense.)

\item Prior research: Which other works have addressed the research question? Which other works have made a relevant assumption? Which other works have used a similar methodology?

The presentation and critical discussion of relevant prior literature serves to contextualize the research question. For any prior literature that is discussed, the paper/thesis makes clear its relevance to the paper/thesis (e.g., to the research question, to the methodology, to the results). Depending on the relationship of the particular work to the research question, the prior work may be just summarized in a single sentence, or may need a paragraph, or even an entire subsubsection. Prior literature that is discussed in more detail is first summarized in a neutral and factual way, and then discussed critically. The summary is detailed enough to allow the reader to understand how the research presented in the work pertains to your research question and to follow your discussion, if there is one. Terminology used in prior literature is defined and illustrated, or (when appropriate) replaced by terminology used in your paper/thesis. Works are summarized and critiqued (e.g., {\em Tonhauser 2018 claimed that...}), not the researchers (e.g., {\em Tonhauser claimed that...}). 

\item Empirical investigation: How did you investigate the research question? What are the results?

The methodology of the empirical investigation is presented in sufficient detail for somebody else to replicate the empirical investigation. 

In the results section, the results are presented in a way that is appropriate for the data collected, i.e., by using the appropriate descriptive statistics (tables and/or figures). The research question is explicitly answered in the results section.

\item Discussion: What are implications of the results? How do the results bear on larger issues around the research question?

The discussion section/chapter briefly reminds the reader of the results of the empirical investigation with respect to the research question and then discusses the implications of the results. For instance, if the investigation provided empirical support for a hypothesis, which hypotheses or research questions might one investigate next? Or, if the investigation provided empirical support against a hypothesis, are there short-comings in the investigation that one might address in future research? Or do the results provide support for a novel hypothesis, to be investigated in future research? See also Rule 8 of the `Ten simple rules for structuring paper/thesis' document. The discussion section/chapter should connect the investigation that is presented in the paper/thesis to the wider body of research discussed in `prior research'.

\item Conclusions: What was investigated and why? What was found?

The concluding section/chapter minimally states the research question and briefly summarizes the results and the implications. It can also mention future research directions or short-comings of the investigation to be rectified in future research. 

\end{itemize}

\end{enumerate}

\item How to summarize prior research

For any linguistics research paper, you will need to provide the reader with information about prior research: in section 1, where introduce and motivate the research question,  and in section 2, where you provide the reader with information about prior research relevant to the research question. There are two questions you should be asking yourself, when thinking about how to inform the reader about prior research:

\begin{enumerate}

\item Why is this research relevant?

Any prior research that you mention in the paper needs to be relevant to the research question. If it is not relevant, you should not mention it. But a prior work can be relevant in different ways: for instance, it can have mentioned that a question is worthy of investigation, it can have made a particular theoretical assumption, it can have used a particular methodology, or it can have investigated the same research question. To identify how you mention the work in your own paper, you need to think about why the paper is relevant. This will determine several things, including: where to introduce the work (sections 1 or 2, or both?), in which detail to introduce the work, and whether your paper should critically discuss/evaluate the work (or just introduce the reader to it/mention it). Ultimately, the reader must be able to understand both what the work was investigating and how their investigation and/or results bear on your paper/thesis.

\item How much detail do I need to provide?

The answer to this question depends on two things: the reader, and why the work is relevant. You cannot assume that the reader is familiar with the prior literature you are considering. This means that, when introducing the reader to prior literature, you continuously have to think about what they need to be introduced to, and whether you have introduced the material in a way that the reader can understand it. It can be helpful to have a specific person in mind, both while writing and while revising the paper. 

How much detail you provide also depends on the role of the prior work with respect to your research question. If, for instance, a particular work is relevant because it has made a particular theoretical assumption and you've already introduced that theoretical assumption to the reader, the work can be mentioned very tersely, for instance in section 1: "For further work that assumes the distinction between factive and non-factive predicates see, for instance, Kiparsky \& Kiparsky 1970". There is no need to provide details on Kiparsky \& Kiparsky 1970, or to critique that work, if all you want to point out is that they make a particular theoretical assumption. This is one end of the spectrum of how much detail to provide. 

On the other end of the spectrum is work that has investigated a research question that is related to (or perhaps even identical to) the research question you are investigating. This work must be discussed in quite some detail so that the reader can understand the work. You may want to mention in section 1 that this is one of the works that have investigated the research question, before presenting the work in detail in section 2. The introduction to the work may need to provide answers to the following questions: which research question did the work investigate?, why did they investigate that question?, how did they investigate the question?, what were the results?, how did the work discuss the results?, what conclusions were drawn? Of course, how much space (how many words) you spend on answering these questions will also need to depend on the overall space you have available for your paper. 

\end{enumerate}


After introducing the reader to the work (and only then!), the work should be critically discussed/evaluated, addressing questions such as: what do you make of the assumptions made in the work?, what do you make of the methodology?, are the results relevant to the research question?, what do you make of the discussion and conclusions? Remember, however, that the discussion should not be based on your ``feelings" or ``thoughts", but it needs to be supported by empirical evidence or other prior literature. 

Usually, the critical discussion would be part of section 2 (or chapter 2, if you're writing a thesis); if, however, you are writing a state-of-the-art paper, the critical discussion should be included in section/chapter 3. 

\end{itemize}

\section{Organization (20 points)}

To receive full credit:

\begin{itemize}[itemsep=-1pt,leftmargin=2.5ex,topsep=-2pt]

\item Papers have sections and subsections; theses have chapters, sections and subsections. Chapters, sections and subsections have informative names that guide the reader.

\item The organization of the paper/thesis into chapters, sections, subsections, etc. aids in guiding the reader, in addition to the paper/thesis telling the reader explicitly what a given chapter, section, or subsection is about, and how it is organized.

\item For a short paper (4,000 words or fewer), do not include an abstract. For a longer paper or a thesis, an abstract should be included and briefly describe the research question and main contributions.

\item Each section/chapter makes a larger point and each subsection makes a smaller point that pertains to the larger point of the section or chapter within
which it is contained. The same goes for paragraphs: each paragraph makes a point that connects to the points made in the previous and the following
paragraphs; the paragraphs within a (sub-)section/chapter jointly contribute to the point of the (sub-)section/chapter.

\item Within a section, chapter or a subsection, the paper/thesis makes explicit how the paragraphs relate to one another. Within a paragraph, the paper/thesis makes explicit how the sentences are connected: for instance, parallel syntactic structures are used for points pertaining to the same question or argument; expressions like {\em however} or {\em but} tell the reader about a contrast; using {\em first...second...finally} guides the reader through points pertaining to the same question or argument. See also Rule 4 of the `Ten simple rules for structuring papers' document.

\item The `Methods' section is clearly organized into the three standard subsections -- for instance, if section 3.1 is the `Methods' section, then the three subsections should be:

\begin{itemize}
\item[3.1.1] Participants
\item[3.1.2] Materials
\item[3.1.3] Procedure
\end{itemize}

Section 3.2 would then be the `Results' section.

\end{itemize}

\section{Mechanics (10 points)}

To receive full credit:

\begin{itemize}[itemsep=-1pt,leftmargin=2.5ex,topsep=-2pt]

\item Your name is stated right below the title of the paper/thesis. 

\item Please state how many ECTS you are writing the paper/thesis for.

\item I expect that you are aware of and follow the university's plagiarism guidelines: \url{https://www.student.uni-stuttgart.de/pruefungsorganisation/document/Leitfaden_Plagiatspraevention_Studierende.pdf}. Term papers and theses should include a signed statement like the following:

{\em I hereby declare that I have written this term paper independently and only using the aids indicated. I have clearly identified as quotes all passages which I have copied verbatim or paraphrased from the literature or from other sources such as websites, and I have given the source.}

\item Font: some standard serif font (e.g., Times New Roman), same font throughout

\item Font size: 11pt or 12pt (including footnotes and references); section and subsection titles and the header of the paper can have a larger font size (e.g., if you're writing the paper in Latex).

\item 2-2.5cm margins 

\item Single line spacing everywhere

\item Footnotes, not endnotes

\item The text is left- and right-aligned.

\item Paper/thesis submitted as PDF (not, e.g., in Word). Theses are also submitted in paper format (see Pr\"ufungsordungen).

\item Figures and tables are consecutively numbered (separately) and have captions.

\item Chapters, sections, subsections and pages are consecutively numbered. Exception: The reference section is not numbered. It comes after the numbered sections, but before any appendices (which include, e.g., experiment materials).

\item Include the word count included (count entire PDF using \url{http://www.montereylanguages.com/pdf-word-count-online-free-tool.html}, do not exclude numbers from word count) and make sure you are not going over the specified word count for the number of credits you are writing for. The abstract and the references do not count for the word count (and neither do appendices).

\item Few to no typos (either British or American English spelling are acceptable, use one consistently)

\item Proper punctuation (e.g., no comma before clause-embedding {\em that})

\item Few to no grammatical errors (I encourage you to use short sentences and to read published literature to identify appropriate phrasings; a great resource for phrasings is here: \url{http://www.phrasebank.manchester.ac.uk/})

\item Chapter, section and subsection numbers and names are consistently formatted; paragraphs are consistently formatted (no indentation of the first paragraph of section, chapter or subsection).

\item Mentioned words are italicized in the running text. Bold-facing can be used, sparingly, for emphasis.

\item The word {\em prove} is not used except to talk about a mathematical proof. In linguistics, we investigate whether there is empirical support for a hypothesis. 

\item The author is referred to in the first person singular, the first person plural, or not at all.

\item Examples are numbered consecutively and formatted according to the Leipzig glossing conventions (\url{https://www.eva.mpg.de/lingua/resources/glossing-rules.php}). Examples in footnotes are numbered using lowercase Roman numerals, rather than Arabic ones; for examples in footnotes, the count is reset to (i) for each footnote.

\item Diacritics like * and \# occur between the example number and the example, as in (\ref{ex}b), not as part of the example, as in (\ref{ex}c).

\begin{exe}
\ex\label{ex}
\begin{xlist}
\ex Nobody has ever slept this long.
\ex \infelic Everybody has ever slept this long.
\ex \#Everybody has ever slept this long.
\end{xlist}
\end{exe}

\item Prior research is discussed in either the present or the past tense (no mixing).

\item Non-English expressions are always translated and the translation occurs in single quotes (e.g., {\em Hund} `dog').

\item Citations in the main body of the paper/thesis as well as in footnotes are properly and consistently formatted (see IfLA document sections 3 and 4). For works with more than two authors, you can use {\em et al.} after the first name instead of spelling out the authors' names. 

\item References are not included in footnotes, but in the (unnumbered) reference section/bibliography.

\item Quotes from other works are properly formatted and attributed (see IfLA document section 4). When you quote a work, the expectation is that you have consulted that work, i.e., are not just reporting somebody else's quote.

\item Examples from other works are properly attributed (with page number), but not placed in quotes. For instance:

\begin{exe}
\ex It is significant that he has been found guilty. \hfill (\citealt[144]{kiparsky-kiparsky70})
\end{exe}

\item Reference section/chapter: References are properly and consistently formatted (see IfLA document section 5; this is a version of the APA style).

\item Theses should include a cover sheet and a table of content; see the IfLA document section 1. For papers, I prefer it if you omit cover sheets (and definitely don't include a table of contents).

\end{itemize}
	
\bibliographystyle{/Users/tonhauser.1/Library/Latex/cslipubs-natbib}
\bibliography{/Users/tonhauser.1/Documents/bibliography}


\end{document}
